\Large \bf Polyglots : Crossing Origins by Crossing Formats

### 2013-02-21 main.tex
Minor edits

\paragraph{HTML comments}
No HTML enclosed in comments, "<--" and "-->", will be rendered, and therefore 
filters consider this context safe. To prevent input from escaping the comment by 
injecting an end comment token, certain filters remove any occurrences of "-->", 
but leave the rest of the input untouched. HTML comments are meaningless to PDF, 
and the result is a valid HTML/PDF polyglot.

>>>>

\paragraph{HTML comments}
No HTML enclosed in comments, "$<$--" and "--$>$", will be rendered, and therefore 
filters consider this context safe. To prevent input from escaping the comment by 
injecting an end comment token, certain filters remove any occurrences of "--$>$", 
but leave the rest of the input untouched. HTML comments are meaningless to PDF, 
and the result is a valid HTML/PDF polyglot.
